---
title: "Text Mining Project_Tibble"
author: "Oluwatobi Ogunronbi"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Step 1: Pre-work

### Installing Packages

```{r}
#install.packages("stringi")
#install.packages("stringr")
#install.packages("qdap")
#install.packages("rJava")
#install.packages("ggthemes")hf
#install.packages("tm")
#install.packages("tidyr")
#install.packages("tidytext")
#install.packages("tidyverse")
#install.packages("ggplot2")
#install.packages("scales")
#install.packages("tokenizers")
#install.packages("reshape2")
#install.packages("tools")
#install.packages("textstem")

```

### Loading installed packages

```{r}
library(stringi)
library(stringr)
library(qdap)
library(rJava)
library(ggthemes)
library(tm)
library(tidyr)
library(tidytext)
library(tidyverse)
library(ggplot2)
library(scales)
library(pdftools)
library(tools)
library(stopwords)
library(readtext)
library(dplyr)
library(tokenizers)
library(SnowballC)
library(textstem)
library(broom)
```

# Step 2: Import the Annual Reports

We'll write a script to recursively list all PDF files within the "DJ-AR" folder, read their contents, and organize them in a tibble with columns for the company name, year, and the text content of each report. Given the folder structure and file naming convention you described, we can extract the year and company abbreviation directly from the filenames.

```{r}
# Path to the DJ-AR folder
pdf_path <- "/Users/bigtobi/Desktop/ITEC_724/final_project/AR_data/DJ-AR"

# Recursively list all PDF files
pdf_files <- list.files(path = pdf_path, pattern = "\\.pdf$", full.names = TRUE, recursive = TRUE)
pdf_filenames <- basename(pdf_files)

print(pdf_filenames)
class(pdf_filenames)
```

```{r}
# Function to parse filename for year and company abbreviation
parse_filename <- function(filename) {
  parts <- str_match(basename(filename), "^(\\d{4})_10K_([A-Za-z]+)")
  if(is.null(parts) || nrow(parts) == 0) {
    year <- NA
    company_abbreviation <- NA
  } else {
    year <- parts[, 2]
    company_abbreviation <- parts[, 3]
  }
  return(tibble(year = year, company_abbreviation = company_abbreviation))
}

# Example file paths for testing
test_filenames <- c("/Users/bigtobi/Desktop/ITEC_724/Project/AR_data/DJ-AR/4_HomeDepot/2022_10K_HD.pdf", "2021_10K_MSFT.pdf", "2022_10K_V.pdf", "NotMatchingFile.pdf")
class(test_filenames)

# Test the parsing function
parsed_test <- map_df(test_filenames, parse_filename)
print(parsed_test)
```

```{r}
# Apply parsing and text extraction using both filenames and full paths
annual_reports <- map_df(1:length(pdf_files), function(idx) {
  # Use pdf_filenames for parsing to get year and company abbreviation
  parsed_info <- parse_filename(pdf_filenames[idx])
  
  # Use pdf_files to extract text content from the PDF
  text_content <- paste(pdf_text(pdf_files[idx]), collapse = " ")
  
  # Combine parsed info with text content into a single tibble row
  parsed_info <- mutate(parsed_info, text_content = text_content)
  
  return(parsed_info)
})

```

View the tibble

```{r}
# View the first few rows of the tibble
head(annual_reports)
#tail(annual_reports)
#class(annual_reports)
```

### Include doc_id in annual reports

```{r}
annual_reports <- mutate(annual_reports,
         doc_id = paste(company_abbreviation, year, sep = "_"))

head(annual_reports)
```

# Create a mapping of company abbreviations and names to their respective industries

```{r}
# Create a mapping of company abbreviations and names to their respective industries
industry_mapping <- data.frame(
  company_abbreviation = c("UNH", "JNJ", "MRK", "AMGN", "MSFT", "AAPL", "CRM", "INTC", 
                           "GS", "V", "JPM", "AXP", "HD", "WMT", "PG", "NKE"),
  company_name = c("UnitedHealth Group", "Johnson & Johnson", "Merck & Co.", "Amgen", 
                   "Microsoft", "Apple", "Salesforce", "Intel Corporation", 
                   "Goldman Sachs", "Visa", "JPMorgan Chase", "American Express", 
                   "Home Depot", "Walmart", "Procter & Gamble", "Nike"),
  industry = c("Healthcare", "Healthcare", "Healthcare", "Healthcare", 
               "Technology", "Technology", "Technology", "Technology", 
               "Financial Services", "Financial Services", "Financial Services", "Financial Services",
               "FMCG", "FMCG", "FMCG", "FMCG")
)

# Join the industry mapping to the 'annual_reports' dataframe
annual_reports <- annual_reports %>%
  left_join(industry_mapping, by = "company_abbreviation")

# Check the first few rows to confirm the join
head(annual_reports)

```

# Step 3: Basic Text Preprocessing
### Cleaning up
```{r}

annual_reports <- annual_reports %>%
  mutate(
    text_content = tolower(text_content),  # Convert text to lowercase
    text_content = str_remove_all(text_content, "[^\\w\\s]"),  # Remove punctuation
    text_content = str_remove_all(text_content, "\\d+")  # Remove numbers
  )

```

# Step 4: Tokenization & TF Analysis
```{r}

# Tokenization and calculating term frequency
tokenized_terms <- annual_reports %>%
  unnest_tokens(word, text_content) %>%
  count(doc_id, industry, company_abbreviation, company_name, year, word, sort = TRUE)  # Count words, grouped by company and year

# View the top terms per company per year
head(tokenized_terms)

```

# Step 5:Developing Custom Stopwords Library
```{r}

custom_stopwords <- c(
  "financial", "fiscal", "firm", "statement", "report", "year", 
  "company", "business", "date", "aa", "income", "stock", "shares", "stocks",
  "management", "operations", "performance", "results", "objective",
  "strategy", "risk", "opportunity", "outlook", "significantly",
  "approximately", "primarily", "including", "regarding", "concerning",
  "due to", "pursuant", "accordance", "thereof", "therein", "hereby",
  "hereto", "hereunder", "usd", "ebitda", "gaap", "qoq", "yoy", "fy",
  "qtr", "one", "two", "first", "second", "third", "quarter", "annual",
  "monthly", "weekly", "day", "month", "year", "law", "regulation",
  "section", "act", "legal", "compliance", "regulatory", "filings",
  "securities", "exchange", "commission", "corporation", "incorporated",
  "plc", "llc", "ltd", "group", "holdings", "united states", "us", "usa",
  "america", "north america", "international", "global", "worldwide", "‰",
  "return", "returns", "eps", "earnings per share", "roe", "return on equity",
  "taxes", "ratio", "cash", "cash flow", "dividend", "revenue", "earnings",
  "expense", "expenses", "asset", "liability", "leverage",
  "patient", "customer", "marketing", "sales",
  "sox", "sec", "sec filing", "ifrs", "audit",
  
  # Company names
  "unitedhealth group", "unitedhealth", "uhg",
  "johnson & johnson", "johnson and johnson", "johnson", "j&j", 
  "merck", "merck & co", "mrk",
  "amgen", "amgn",
  "microsoft", "msft",
  "apple", "aapl",
  "salesforce", "crm",
  "intel", "intel corporation", "intc",
  "goldman sachs", "goldman", "gs", "sachs",
  "visa", "v",
  "jpmorgan chase", "jpmorgan", "jpm", "chase",
  "american express", "amex", "axp",
  "home depot", "hd",
  "walmart", "wmt",
  "procter & gamble", "pg", "p&g", "procter", "gamble",
  "nike", "nke"
)

# Create a tibble for custom stopwords to match tidytext format
custom_stopwords_df <- tibble(word = custom_stopwords, lexicon = "custom")

# Combine custom stopwords with standard English stopwords
all_stopwords <- bind_rows(stop_words, custom_stopwords_df)
```

#Remove Stopwords
#### From tokenized
```{r}
# Removing stopwords
clean_terms <- tokenized_terms %>%
  anti_join(all_stopwords, by = "word")

head(clean_terms)
tail(clean_terms)
```
#### From untokenized
```{r}
# Let's first tokenize the text content

# Tokenize the text content
full_tokens <- annual_reports %>%
  unnest_tokens(word, text_content)

# Ensure all tokens are lowercase (assuming your stopwords are all lowercase)
#tokens$word <- tolower(tokens$word)

# Load standard English stopwords from the tidytext package
#data("stop_words")

# Combine custom stopwords with tidytext's stopwords if you have custom ones
# custom_stopwords <- tibble(word = c("your", "custom", "stopwords", "..."))
# all_stopwords <- bind_rows(stop_words, custom_stopwords)

# Now, filter out the stopwords from the tokens
clean_full_tokens <- full_tokens %>%
  anti_join(all_stopwords, by = "word")

# If you need to reassemble the cleaned text for each document:
clean_annual_reports <- clean_full_tokens %>%
  group_by(doc_id, industry, year, company_abbreviation, company_name) %>%
  summarize(text_content = paste(word, collapse = " ")) %>%
  ungroup()

head(clean_annual_reports)

# clean_annual_reports now contains the cleaned text_content without stopwords
```

# Research Question 1

### Term Frequency-Inverse Document Frequency (TF-IDF) for the words across the annual reports

```{r}

# Document Frequency (DF)
# Count how many documents each word appears in
document_freq <- clean_terms %>%
  group_by(word) %>%
  summarise(n_docs = n_distinct(year))

# 3. Inverse Document Frequency (IDF)
# Calculate IDF
total_documents <- n_distinct(clean_terms$year)
idf <- mutate(document_freq, idf = log(total_documents / n_docs))

# 4. TF-IDF Calculation
# Join TF and IDF values and calculate TF-IDF
tf_idf <- clean_terms %>%
  inner_join(idf, by = "word") %>%
  mutate(tf_idf = n * idf)

# Optional step: Remove extremely common words if necessary
tf_idf <- tf_idf %>%
  filter(!word %in% c("the", "of", "and", "to", "in", "for", "on", "with", "as", "by"))

# Sort by TF-IDF to find the most important words
tf_idf <- tf_idf %>%
  arrange(desc(tf_idf))

# View the results
head(tf_idf)
tf_idf

```


The head of the tf_idf tibble points to terms with high TF-IDF scores, highlighting words like "licence" and "commercialisation" for AMGN in 2023, and "series" and "swing" for companies like GS and V in various years. High scores signify these terms' uniqueness or emphasis within particular documents, indicating a specific focus for those companies in those years. For example, the unique terms for AMGN suggest a focus on licensing and commercialization in 2023. The term "series" for GS, despite appearing in several documents, still garners a significant score, suggesting a potential emphasis on financial instruments or classifications like series bonds or stock series.

Conversely, the tail of the tf_idf tibble showcases terms with lower TF-IDF scores, which include "commodities," "financings," and "arbitration." These terms are more common across multiple documents and do not feature prominently within any single report. Their presence across various documents reduces their TF-IDF score, implying they are part of the standard lexicon in annual reports and are not indicative of particular corporate priorities or trends.

In synthesis, the high TF-IDF terms are potentially more informative about a company's strategic focus in a given year, hinting at specific initiatives or concerns that are top of mind. They warrant further investigation into the context of their usage within the reports. Low TF-IDF terms, while relevant to the industry and necessary in reporting, offer less in the way of distinguishing between the strategic directions of different companies or identifying sector-wide trends. They serve as background industry language that, while important, is not as indicative of individual company focus or unique industry developments.

#### Bar Chart for Top TF-IDF Scores
```{r}

# Let's take the top 10 words for simplicity
top_tfidf <- tf_idf %>%
  arrange(desc(tf_idf)) %>%
  top_n(10, tf_idf)

# Create a bar chart
ggplot(top_tfidf, aes(x = reorder(word, tf_idf), y = tf_idf, fill = industry)) +
  geom_bar(stat = "identity") +
  coord_flip() +  # Flip coordinates to make it easier to read long words
  labs(title = "Top TF-IDF Scores by Word",
       x = "Term",
       y = "TF-IDF Score") +
  theme_minimal() +
  scale_fill_brewer(palette = "Paired")  # Optional: use a color palette for visual distinction

```
#### Heatmap of TF-IDF by Company and Year
```{r}

# Assuming `tf_idf` is your dataframe with the TF-IDF results
# Select the top 10 words by TF-IDF score
top_terms <- tf_idf %>%
  arrange(desc(tf_idf)) %>%
  slice(1:30) %>%
  .$word  # Extract just the words

# Filter the original tf_idf data to only include the top terms
top_tfidf <- tf_idf %>%
  filter(word %in% top_terms)

# Create the heatmap
ggplot(top_tfidf, aes(x = year, y = word, fill = tf_idf)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "blue") +
  labs(title = "Top 10 TF-IDF Terms by Year",
       x = "Year",
       y = "Term",
       fill = "TF-IDF Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))  # Rotate x labels for better readability

```
When taken together, these visualizations reveal both the overall importance of certain terms within the corpus (bar chart) and their specific relevance across different temporal segments (heatmap). For example, while "licence" has a significant TF-IDF score overall, it is particularly dominant in one year, suggesting a pivotal event or initiative related to licensing in that year.

The use of terms such as "commercialisation," "series," and "swing" across several years points to ongoing strategic themes within their respective industries. Conversely, some terms appear to be more transient, emerging strongly in one year and fading in others, potentially reflecting temporary strategic shifts, market conditions, or regulatory changes.


### N-Grams Analysis

#### Bigrams analysis
```{r}

# Generate bigrams
bigrams <- annual_reports %>%
  unnest_tokens(bigram, text_content, token = "ngrams", n = 2) %>%
  group_by(doc_id, industry, company_name, year) %>%
  count(bigram, sort = TRUE) %>%
  ungroup() %>%
  separate(bigram, into = c("word1", "word2"), sep = " ") %>%
  mutate(bigram = paste(word1, word2, sep = " ")) %>%  # Add this line to reassemble bigrams
  #select(-word1, -word2) %>%  # Remove individual word columns
  anti_join(all_stopwords, by = c("word1" = "word")) %>%
  anti_join(all_stopwords, by = c("word2" = "word"))


# View the most common bigrams (adjust as necessary for specific analyses)
head(bigrams)
#class(bigrams)
#bigrams[bigrams$word1 == "goldman"]
```

#### Bigrams Plot
```{r}

# Aggregate bigram counts across all industries and years
aggregated_bigrams <- bigrams %>%
  group_by(word1, word2) %>%
  summarize(n = sum(n), .groups = 'drop') %>%
  arrange(desc(n))

# Take the top 10 bigrams for visualization
top_bigrams <- head(aggregated_bigrams, 10)

# Combine word1 and word2 into a bigram column for the top bigrams
top_bigrams <- top_bigrams %>%
  unite("bigram", word1, word2, sep = " ")

# Plot the top bigrams
ggplot(top_bigrams, aes(x = reorder(bigram, n), y = n, fill = bigram)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = NULL, y = "Frequency", title = "Top 10 Bigrams in the Corpus") +
  theme_minimal() +
  theme(legend.position = "none")

```

#### Trigrams analysis
```{r}
# Generate trigrams
trigrams <- annual_reports %>%
  unnest_tokens(trigram, text_content, token = "ngrams", n = 3) %>%
  select(doc_id, industry, company_name, year, trigram) %>%
  count(doc_id, industry, company_name, year, trigram, sort = TRUE)

# Separate the trigram into three words
trigram_separated <- trigrams %>%
  separate(trigram, into = c("word1", "word2", "word3"), sep = " ")

# Filter out trigrams that have stopwords as any word if necessary
trigram_separated <- trigram_separated %>%
  anti_join(all_stopwords, by = c("word1" = "word")) %>%
  anti_join(all_stopwords, by = c("word2" = "word")) %>%
  anti_join(all_stopwords, by = c("word3" = "word"))

# View the most common trigrams
print(trigram_separated)
print(trigrams)
```

#### Trigrams Plot
```{r}
# Aggregate trigram counts across all industries and years
aggregated_trigrams <- trigram_separated %>%
  group_by(word1, word2, word3) %>%
  summarize(n = sum(n), .groups = 'drop') %>%
  arrange(desc(n))

# Take the top trigrams for visualization
top_trigrams <- head(aggregated_trigrams, 10)

# Combine the separated words back into a trigram column for the top trigrams
top_trigrams <- top_trigrams %>%
  unite("trigram", word1, word2, word3, sep = " ")

# Plot the top trigrams
ggplot(top_trigrams, aes(x = reorder(trigram, n), y = n, fill = trigram)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = NULL, y = "Frequency", title = "Top 10 Trigrams in the Corpus") +
  theme_minimal() +
  theme(legend.position = "none")

```
# Research Question 3
#### Bigrams For one industry
```{r}

# Step 1: Generate bigrams
bigrams3 <- clean_annual_reports %>%
  unnest_tokens(bigram, text_content, token = "ngrams", n = 2) %>%
  group_by(doc_id, industry, year) %>%
  ungroup()

# Step 2: Count the frequency of bigrams within each industry
bigram_freq <- bigrams3 %>%
  count(doc_id, industry, company_abbreviation, bigram) %>%
  anti_join(all_stopwords, by = c("bigram" = "word"))


# Steps 3-4: Calculate the number of documents per industry that each bigram appears in
bigram_document_freq <- bigram_freq %>%
  group_by(bigram, industry) %>%
  summarize(n_docs = n_distinct(doc_id)) %>%
  ungroup() %>%
  left_join(bigram_freq %>%
              group_by(industry) %>%
              summarize(total_docs = n_distinct(doc_id)) %>%
              ungroup(),
            by = "industry") %>%
  mutate(idf = log(total_docs / n_docs),
         total_docs = NULL)

# Steps 5-6: Calculate TF-IDF
tf_idf_by_industry <- bigram_freq %>%
  left_join(bigram_document_freq, by = c("bigram", "industry")) %>%
  mutate(tf_idf = n * idf)

# Steps 7-8: Filter and view the top bigrams for a single industry
top_tfidf_financial <- tf_idf_by_industry %>%
  arrange(desc(tf_idf)) %>%
  group_by(industry) %>%
  top_n(15, tf_idf) %>%
  ungroup() %>%
  filter(industry == "Financial Services")

# Step 9: Visualize the top TF-IDF bigrams for the financial industry
ggplot(top_tfidf_financial, aes(x = reorder(bigram, tf_idf), y = tf_idf, fill = industry)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "Bigram", y = "TF-IDF Score", title = "Top TF-IDF Bigrams in Financial Services") +
  theme_minimal()

```


#### Bigrams for all industry
```{r}

# Steps 7-8: Filter and view the top bigrams for all industries
top_tfidf_all <- tf_idf_by_industry %>%
  arrange(industry, desc(tf_idf)) %>%
  #arrange(industry) %>%
  group_by(industry) %>%
  top_n(5, tf_idf) %>%
  ungroup()

# Filter s
# Step 9: Visualize the top TF-IDF bigrams for all industries
ggplot(top_tfidf_all, aes(x = reorder(bigram, tf_idf), y = tf_idf, fill = industry)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = "Bigram", y = "TF-IDF Score", title = "Top TF-IDF Bigrams by Industry") +
  theme_minimal()

```

#### Bigrams for companies
```{r}

# Assuming 'bigrams' contains your bigram data with 'company_abbreviation' and 'industry' columns.
# First, count the bigrams for each company's documents.
bigram_counts <- bigrams %>%
  count(company_name, bigram, sort = TRUE)

# Calculate the document frequency for each bigram across all companies.
document_freq <- bigram_counts %>%
  group_by(bigram) %>%
  summarize(n_docs = n_distinct(company_name)) %>%
  ungroup()

# Calculate IDF for each bigram.
idf <- document_freq %>%
  mutate(idf = log(n_distinct(bigrams$company_name) / n_docs))

# Join with the bigram counts to calculate the TF-IDF score for each bigram in each company's documents.
tf_idf <- bigram_counts %>%
  left_join(idf, by = "bigram") %>%
  mutate(tf_idf = n * idf)

# Now, select the top bigrams for each company based on the TF-IDF score.
top_tfidf_by_company <- tf_idf %>%
  group_by(company_name) %>%
  top_n(3, tf_idf) %>%
  ungroup()

# Optionally, you can also join back with the industry information if needed.
top_tfidf_by_company <- top_tfidf_by_company %>%
  left_join(bigrams %>% select(company_name, industry) %>% distinct(), by = "company_name")

# Now you can view or save the result
print(head(top_tfidf_by_company))
print(tail(top_tfidf_by_company))

# Create a summary table for the top bigrams by company
summary_table <- top_tfidf_by_company %>%
  arrange(industry, company_name, desc(tf_idf)) %>%
  group_by(industry, company_name) %>%
  slice_max(order_by = tf_idf, n = 3) %>%
  ungroup() %>%
  select(company_name, bigram, tf_idf)

# Print the table to the R console
#print(summary_table)

# If the table is too large, you can use the `head` function to display the first few rows
print(head(summary_table))
print(tail(summary_table))

# Or write it out to a CSV file for opening in Excel or similar
#write.csv(summary_table, "top_bigrams_by_company.csv", row.names = FALSE)

```
#### Trigrams
```{r}

# View the top trigrams for each company
top_trigrams_by_company <- trigram_separated %>%
  group_by(company_name) %>%
  top_n(1, n) %>%
  ungroup()

# Print the top trigrams for each company
print(top_trigrams_by_company)

```

# Research Question 2

#### Sentiment Analysis per Company

```{r}

# Assuming 'annual_reports' has columns 'text_content', 'company_abbreviation', and 'year'

# Step 1: Unnest text content into sentences or words
words <- annual_reports %>%
  unnest_tokens(word, text_content)

# Step 2: Get sentiment scores using a sentiment lexicon
sentiment_lexicon <- get_sentiments("afinn")  # bing or AFINN
sentiment_scores <- inner_join(words, sentiment_lexicon, by = "word")

sentiment_scores

# Step 3: Aggregate sentiment scores by year (and company if needed)
annual_sentiment <- sentiment_scores %>%
  group_by(year, company_name, company_abbreviation) %>%
  summarize(sentiment_score = sum(value), .groups = 'drop')

# Step 4: Create a time-series plot for sentiment over time
ggplot(annual_sentiment, aes(x = year, y = sentiment_score, group = company_name, color = company_name)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Annual Sentiment in Reports", x = "Year", y = "Sentiment Score")

# Alternative plot
ggplot(annual_sentiment, aes(x = year, y = sentiment_score, group = company_name, color = company_name)) +
  geom_line() +
  facet_wrap(~company_name, scales = "free_y", ncol = 4) +  # Adjust the number of columns as needed
  theme_minimal() +
  labs(title = "Annual Sentiment in Reports over 5 FYs", x = "Year", y = "Sentiment Score") +
  theme(#strip.text = element_blank(),  # Remove facet labels
        axis.text = element_blank(),   # Remove axis text
        axis.title = element_blank()
        ) +  # Remove axis titles
  guides(color = FALSE)
  

# This will plot sentiment trends for each company. To see industry-wide trends, group by industry.

```


#### Sentiment Analysis by Industry
```{r}
# Aggregate sentiment scores by year and industry
annual_sentiment_by_industry <- sentiment_scores %>%
  group_by(year, industry, company_name, company_abbreviation) %>%
  summarize(sentiment_score = sum(value), .groups = 'drop')

# Create a time-series plot for sentiment over time by industry
ggplot(annual_sentiment_by_industry, aes(x = year, y = sentiment_score, group = industry, color = industry)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Annual Sentiment in Reports by Industry", x = "Year", y = "Sentiment Score") +
  facet_wrap(~ industry, scales = "free_y", ncol = 1) + # Adjust the number of columns as needed
  guides(color = FALSE)
```

# Research Question 4: 
#### Analysis
```{r}

# Assuming you have a sentiment score calculated and 'industry' variable in your dataset

# Step 1: Aggregate sentiment scores by company within each industry
sentiment_by_company_industry <- sentiment_scores %>%
  group_by(industry, company_name) %>%
  summarize(mean_sentiment = mean(value), .groups = 'drop')

# Step 2: Perform sub-group comparisons within each industry
# Note: This can be a visualization or a statistical test depending on the depth of analysis required

# Alternative Plot
ggplot(annual_sentiment_by_industry, aes(x = year, y = sentiment_score, group = company_name, color = industry)) +
  geom_line() +
  geom_text(data = annual_sentiment_by_industry %>% group_by(company_name) %>% filter(year == max(year)),
            aes(label = company_abbreviation), 
            hjust = 1.1, vjust = 0, 
            size = 3,
            color = "black",
            check_overlap = TRUE, 
            angle = 0) +  # adjust the angle if needed
  theme_minimal() +
  labs(title = "Annual Sentiment in Reports", x = "Year", y = "Sentiment Score") +
  facet_wrap(~ industry, scales = "free_y") +
  theme(legend.position = "none")  # This will remove the legend


# For Statistical Testing (e.g., ANOVA):
# Assuming sentiment_scores also has 'value' as the sentiment score column
anova_results <- sentiment_by_company_industry %>%
  group_by(industry) %>%
  do(tidy(aov(mean_sentiment ~ company_name, data = .)))

anova_results

# Step 3: Interpret the results
# Depending on the outcome of the visualization or statistical test, draw conclusions about 
# the different strategic postures or conditions of companies within the same industry.

```

